Different forms of uncertainty differently affect the evolution of social learning

### 2022-08-25 ms.tex
addressed some comments in model

A population of $N$ individuals each must decide which of $B$ behaviors to perform at
each time step within a generation consisting of $L$ time steps. The behavior set is a multi-armed bandit with $B$ arms, that is, agents can pick one of $B$ behaviors with random-valued payoffs~\cite{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}. \ps{To clarify terminology, the entire set of behaviors is one multi-armed bandit with $B$ arms -- each behavior is not itself a bandit.} 
%Each behavior yields a payoff of either 1 or 0 with some probability that is held fixed within a generation but can change between generations. This probability is therefore equal to the behavior's expected payoff within a generation. 
In each generation, exactly one behavior is more likely to pay off than all the rest and is therefore optimal. Agents
optimize their net payoffs over their lifespan by quickly figuring out which
behavior is optimal and performing it as often as possible within their lifespan.
%The optimal behavior is static within agent lifespans, but varies in general between generations, representing environmental variability.
At the end of each
generation, agents are selected with replacement to reproduce a new generation of $N$ agents, with the probability of reproduction biased by net payoffs. Agents who inherit the social learning trait learn about payoffs from the previous generation, while asocial learners begin life with no \emph{a priori}
knowledge of the world. \cm{or would you consider having flat priors over all behaviors knowledge?}  
%The specifics of the model construction and dynamics are described in detail below.
\ps{I cut a bunch of stuff that came right here as being redundant or unnecessary.}

@@

\paragraph{Intergenerational dynamics}
Between generations, agents first reproduce via asexual haploid reproduction, which determines the transmission of the social learning trait. Social learners then learn from the
previous generation, after which all agents from the
previous generation die off (Figure~\ref{fig:schematic}C). More specifically, this all happens as follows. 
$N$ reproducers are selected with replacement over $N$ independent draws, 
biased by performance:
\begin{equation}
  \Pr(\text{Agent $i$ is chosen to reproduce in one draw}) = \frac{\pi_i}{\sum_{i=1}^N \pi_i}.
\end{equation}
\noindent
A child inherits its parent's social learning trait $s_i$ without mutation.
A social learner child with $s_i = 1$ learns from a teacher from its parent's
generation, including possibly their parent (i.e., both vertical and oblique learning are possible). 
A child chooses its teacher by first randomly selecting $N_T$ prospective
teachers from the population, then selecting the one with
highest net payoffs $\pi_i$ as their teacher, with ties broken randomly \cm{this seems to contradict info under 2.2.2 Social learning section where there seems to be a probabilistic element weighted by relative payoff of teachers. I think it doesn't have to be described in both places.}. By first subsetting $N_T$ prospective teachers we represent the fact that access to the entire population is not generally guaranteed, though this type of algorithm yields qualitatively similar results to ones that do not first produce subsamples \cite{smaldino2019open}. 
Social learners adopt their chosen teacher's expected payoffs observations $\ledger$, \ps{I feel like there should be some indication that the ledger is a vector rather than a scalar. Maybe put it in bold or capitalize the $\Pi$? Using the overbar makes it look like a single average.}
and set all $c_{ib} = 1$ so expected payoffs remain within $[0, 1]$. Setting $c_{ib}$ to 1 reflects the fact that the social learning is treating the teacher's information as a single observation with the associated uncertainty.   Asocial
learners ($s_i = 0$) are initialized with $c_{ib} = 0$ and $\ledger = 0$ 
(Figure~\ref{fig:schematic}C). \ps{How to account for division by zero?} The
newly initialized population then repeats the within-generation dynamics.

@@

\paragraph{Stopping conditions} The evolutionary process continues until the
population reaches evolutionary fixation with repsect to social learning, where
$\sum_i s_i = 1$ or $\sum_i s_i = 0$, or until 20k iterations have run. 
It is rare for simulations not to reach fixation. We report how frequently
this happens in Table~\ref{tab:convergence}. \ps{Supplementary figures and table should be prefixed with an ``S."}

>>>>

A population of $N$ individuals each must decide which of $B$ behaviors to perform at
each time step within a generation consisting of $L$ time steps. The behavior set is a multi-armed bandit with $B$ arms, that is, agents can pick one of $B$ behaviors with random-valued payoffs~\cite{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}.  
In each generation, exactly one behavior is more likely to pay off than all the rest and is therefore optimal. Agents
optimize their net payoffs over their lifespan by quickly figuring out which
behavior is optimal and performing it as often as possible within their lifespan.
%The optimal behavior is static within agent lifespans, but varies in general between generations, representing environmental variability.
At the end of each
generation, agents are selected with replacement to reproduce a new generation of $N$ agents,
with the probability of reproduction biased by net payoffs. Agents who inherit the social
learning trait learn about payoffs from the previous generation, while asocial learners begin
life only knowing the number of behaviors the environment affords, but no knowledge
of behavioral payoffs.
\cm{or would you consider having flat priors over all behaviors knowledge?} 
\mt{I changed this last sentence to express that they have flat priors, in somewhat different
terms.}
%The specifics of the model construction and dynamics are described in detail below.
% \ps{I cut a bunch of stuff that came right here as being redundant or unnecessary.}

@@

\paragraph{Intergenerational dynamics}
Between generations, agents first reproduce via asexual haploid reproduction, which determines the transmission of the social learning trait. Social learners then learn from the
previous generation, after which all agents from the
previous generation die off (Figure~\ref{fig:schematic}C). More specifically, this all happens as follows. 
$N$ reproducers are selected with replacement over $N$ independent draws, 
biased by performance:
\begin{equation}
  \Pr(\text{Agent $i$ is chosen to reproduce in one draw}) = \frac{\pi_i}{\sum_{i=1}^N \pi_i}.
\end{equation}
\noindent
A child inherits its parent's social learning trait $s_i$ without mutation.
A social learner child with $s_i = 1$ learns from a teacher from its parent's
generation, including possibly their parent (i.e., both vertical and oblique learning are possible). 
A child chooses its teacher by first randomly selecting $N_T$ prospective
teachers from the population, then selecting the one with
highest net payoffs $\pi_i$ as their teacher, with ties broken randomly \cm{this seems to contradict info under 2.2.2 Social learning section where there seems to be a probabilistic element weighted by relative payoff of teachers. I think it doesn't have to be described in both places.}. By first subsetting $N_T$ prospective teachers we represent the fact that access to the entire population is not generally guaranteed, though this type of algorithm yields qualitatively similar results to ones that do not first produce subsamples \cite{smaldino2019open}. 
Social learners adopt their chosen teacher's expected payoffs observations $\ledger$, \ps{I feel
like there should be some indication that the ledger is a vector rather than a scalar. Maybe put
it in bold or capitalize the $\Pi$? Using the overbar makes it look like a single average.}
\mt{The subscript $b$ makes it clear it's a vector over behaviors. Maybe we lose the bar,
or I may change the notation to at least approximately follow Q-learning notation.}
and set all $c_{ib} = 1$ so expected payoffs remain within $[0, 1]$. Setting $c_{ib}$ to 1 reflects the fact that the social learning is treating the teacher's information as a single observation with the associated uncertainty.   Asocial
learners ($s_i = 0$) are initialized with $c_{ib} = 0$ and $\ledger = 0$ 
(Figure~\ref{fig:schematic}C). \ps{How to account for division by zero?} \mt{Count increases
before average are taken, which I think is clear enough in paragraph \textbf{Within-generation
dynamics}.} The
newly initialized population then repeats the within-generation dynamics.

@@

\paragraph{Stopping conditions} The evolutionary process continues until the
population reaches evolutionary fixation with repsect to social learning, where
$\sum_i s_i = 1$ or $\sum_i s_i = 0$, or until 20k iterations have run. 
It is rare for simulations not to reach fixation. We report how frequently
this happens in Table~\ref{tab:convergence}.
